\section{Apple Pie}
\label{applePie}
\setcounter{secnumdepth}{0}
Time: 1 hour 20 minutes (30 minutes prep, 50 minutes baking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 recipes of \nameref{pieCrust}.
    \item 4-5 pounds of apples (mix of grannysmith, honeycrisp, and envy), peeled and sliced fairly thin.
    \item 3 \( \frac{1}{2} \) ounces (about \( \frac{1}{2} \) cups) granulated sugar
    \item 2 ounces (about \( \frac{1}{4} \) cup) dark brown sugar
    \item 1 \( \frac{1}{2} \) ounces (about \( \frac{1}{4} \) cup) all purpose flour
    \item \( \frac{1}{4} \) teaspoon cinnamon
    \item \( \frac{1}{4} \) teaspoon nutmeg
    \item \( \frac{1}{4} \) teaspoon grains of paradise (ground)
    \item \( \frac{1}{2} \) ounces (1 Tablespoon) butter, melted
    \item 1 teaspoon granulated sugar
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Pie pan
    \item Mixing bowl
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Make a double recipe of pie crust, following the standard recipe. Once you get to the 30 minutes resting in the fridge, begin making the apple filling for the pie.
    \item Preheat oven to 400F.
    \item COmbine 4-5 pounds of sliced apples, 3 \( \frac{1}{2} \) ounces sugar, 2 ounces dark brown sugar, 1 \( \frac{1}{2} \) ounces all purpose flour, \( \frac{1}{4} \) teaspoon cinnamon, \( \frac{1}{4} \) teaspoon nutmeg, and \( \frac{1}{4} \) teaspoon grains of paradise in a mixing bowl.
    \item Spread one of the pie crusts in a pie pan.
    \item Roll out a second crust and cut into \( \frac{1}{2} \) inch strips.
    \item Spread the filling into the pie crust.
    \item Create a lattice with the crust strips over the apples.
    \item Trim the edges of the crust to be smooth and crimp down with your fingers.
    \item Brush \( \frac{1}{2} \) ounces melted butter over the crust.
    \item Sprinkle 1 teaspoon sugar over the crust.
    \item Bake for 15 minutes at 400F.
    \item Turn the heat down to 350F and allow to finish baking, about 35 minutes.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is my own apple pie recipe, however I got the idea for grains of paradise from Alton Brown.
    \item I don't bother with the rest of Alton Brown's recipe (\url{https://altonbrown.com/apple-pie-recipe/}. It looks good, but is tons of trouble, and I don't own a pie bird (though I'd love a pie llama).
\end{itemize}
\end{multicols}
\clearpage