\section{Banana Pudding (refrigerated)}
\label{bananaPudding}
\setcounter{secnumdepth}{0}
Time: 2 hours (30 minutes prep, 1 hour 30 minutes making the parts)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item Double recipe of \nameref{cremePatissiere}, but remove from heat a little early to keep it slightly less set than normal.
    \item 3 Large barely green bananas, sliced into quarter inch rounds
    \item 1 Tablespoon lemon juice
    \item 1 recipe of \nameref{vanillaWafers}
    \item 1 recipe of \nameref{whippedCream}
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Large Mixing bowl
    \item Silicone spatula
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Place a very small layer of the crème pâtissière at the bottom of the mixing bowl.
    \item Make a layer of vanilla wafers.
    \item Make a layer of banana slices on top of that.
    \item Put about (\( \frac{1}{3} \) of the crème pâtissière on top of this.
    \item Repeat the above 3 steps twice to get a bowl full of pudding.
    \item Speard the whipped cream over the top.
    \item Place 8-10 vanilla wafers vertically in the top of the whipped cream.
    \item Enjoy within 3 days.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Based on the Alton Brown's recipe, as seen here: \url{https://www.foodnetwork.com/recipes/alton-brown/refrigerated-banana-pudding-recipe-1920910}.
    \begin{itemize}
        \item Main differences are lack of banana liquer (no need, it's moist enough), and I use an actual crème pâtissière instead of Alton Brown's pudding base. While his pudding base was essentially a custard (and nearly a crème pâtissière), I prefer the heavier, egg-rich crème pâtissière.
    \end{itemize}
    \item Banana pudding works amazingly well as a dessert after barbecue.
    \item Banana pudding is a quintessential southern dessert, to the point where when I first mentioned it in an office in Seattle no one knew what it was except my manager from Mississippi.
    \item I prefer refrigerated banana pudding, though there is also a baked version that is quite delicious.
\end{itemize}
\end{multicols}
\clearpage