\section{Buttermilk Pie}
\label{buttermilkPie}
\setcounter{secnumdepth}{0}
Time: 1 \( \frac{1}{2} \) hours (30 minutes prep, 1 hours baking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 3 eggs
    \item \( \frac{1}{2} \) cup butter, softened (for creaming)
    \item 1 \( \frac{1}{2} \) cups sugar
    \item 3 tablespoons all-purpose flour
    \item 1 cup buttermilk
    \item 1 teaspoon vanilla extract
    \item 1 tablespoon fresh lemon juice
    \item \( \frac{1}{8} \) teaspoon nutmeg
    \item 1 pie crust (see \nameref{pieCrust} recipe)

\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Pie pan
    \item Mixing bowl
    \item Whisk/Paddle
    \item Silicone spatula
    \item Small bowl
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Make a pie crust, following the standard recipe. Once you get to the 30 minutes resting in the fridge, begin making the custard filling for the buttermilk pie.
    \item Preheat oven to 325F.
    \item Beat 3 eggs until frothy.
    \item Add 1 \( \frac{1}{2} \) cups sugar, 3 tablespoons flour, and \( \frac{1}{2} \) cup softened butter.
    \item Mix immediately upon adding butter until smooth.
    \item Add 1 teaspoon vanilla extract.
    \item Combine 1 cup buttermilk, 1 tablespoon lemon juice, and \( \frac{1}{8} \) teaspoon nutmeg in a small bowl.
    \item Add buttermilk mixture to egg mixture and stir to combine.
    \item Pour mixture into pie crust.
    \item Bake for 45-70 minutes, until center is fairly firm.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is Cyndy Watt’s recipe, just like she made it when I was growing up.
    \item You can make 2 pies with this same amount in more shallow pie-pans. This reduces the cook time.
    \item You may need to cover the edge of the pie crust during baking, especially if it takes more than 50 minutes or so to set. I use pieces of aluminum foil to cover the crust.
    \item I’m still experimenting with heat and time levels for the standard depth of pie. I was making 2 shallow pies for years due to my pie pans.

\end{itemize}
\end{multicols}
\clearpage