\section{Rice Krispy Treats}
\label{riceKrispyTreats}
\setcounter{secnumdepth}{0}
Time: 45 minutes (5 minutes cooking, 40 minutes cooling)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 ounces unsalted butter
    \item 10 ounces marshmallows
    \item 6 ounces rice krispies
    \item OPTIONAL: 5 ounces peanut butter, and use just shy of 2 ounces butter instead
    \item butter or cooking spray for greasing
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Large non-stick stock pot
    \item Silicone spatula
    \item 9x9 Baking dish
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Bring 2 ounces butter to a slight bubble over medium-low heat in a stock pot (or about 1.4 ounces if adding peanut butter).
    \item While the butter is heating, lightly grease a 9x9 baking dish with butter or cooking spray.
    \item Add 10 ounces marshmallows and stir until the marshmallows are completely melted and smooth, about 4 minutes.
    \item OPTIONAL, if adding peanut butter, Add 5 ounces peanut butter to the marshmallow mixture and stir to combine.
    \item Add 6 ounces Rice Krispies and fold into the marshmallow mixture.
    \item Once all Rice Krispies are evenly coated, dump the mixture into a 9x9 baking dish and press down with a spatula or wax paper to make sure all contents are pressed together.
    \item Chill for at least 30 minutes in the fridge prior to serving.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Based on the Kellog's recipe, as seen here: \url{https://www.ricekrispies.com/en_US/recipes/the-original-treats-recipe.html}.
    \begin{itemize}
        \item Main differences are increased butter, optional peanut butter, and changed all ingredients to weight instead of volume.
    \end{itemize}
    \item This can be modified pretty easily, add M\&M's, put melted chocolate on top before cooling, replace cereal with Fruity Pebble's, etc.
    \item This can be spread into a 9x13 baking dish for thinner treats that also cool faster, but I like them thick.
\end{itemize}
\end{multicols}
\clearpage