\section{Vanilla Wafers}
\label{vanillaWafers}
\setcounter{secnumdepth}{0}
Time: 45 minutes (15 minutes prep, 10 minutes cooling, 20 minutes baking)
Serves: 35-40 cookies

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 7 ounces all-purpose flour
    \item \( \frac{3}{4} \) teaspoons aluminum-free baking soda
    \item \( \frac{1}{2} \) teaspoons kosher salt
    \item 4 ounces unsalted butter, room temperature
    \item 3 \( \frac{1}{2} \) ounces \nameref{vanillaSugar}
    \item 1 large egg
    \item 4 teaspoons vanilla extract
    \item 1 Tablespoon whole milk
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Electric Mixer
    \item Small mixing bowl
    \item Large mixing bowl
    \item Parchment Paper
    \item 2 Cookie sheets
    \item Cookie cooling rack
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Position oven rack in the top \( \frac{1}{3} \) of the oven and the other in the bottom \( \frac{1}{3} \).
    \item Preheat oven to 350F.
    \item Sift 7 ounces flour, \( \frac{3}{4} \) teaspoons baking soda, and \( \frac{1}{2} \) teaspoons salt, set aside.
    \item Cream 4 ounces butter and 3 \( \frac{1}{2} \) ounces vanilla sugar for 2 minutes on medium, stopping to scrape down the sides if necessary.
    \item Add 1 egg and mix for 30 seconds.
    \item Scrape down the dough mixture.
    \item Add 4 teaspoons vanilla extract and 1 tablespoon milk, mix on low for 15 seconds.
    \item Add dry mixture and mix on low just to incorporate.
    \item Chill the batter for at least 10 minutes to let it rest and be slightly less sticky.
    \item Scoop the batter into teaspoon-sized balls, arranged on 2 sheets of parchment paper-lined baking sheets.
    \item Slightly flatten the balls with your hand.
    \item Bake both pans, rotating halfway through, until golden brown, for 15 - 20 minutes.
    \item Remove pans and allow to cool completely before removing the cookies.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is Alton Brown’s recipe, as seen here: \url{https://www.foodnetwork.com/recipes/alton-brown/vanilla-wafers-recipe-1920909}.
\end{itemize}
\end{multicols}
\clearpage