\section{Broccoli Cheddar Soup}
\label{broccoliCheddarSoup}
\setcounter{secnumdepth}{0}
Time: 40 minutes (10 minutes prep, 30 minutes cooking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item Double recipe of a white \nameref{roux}
    \item 32 ounces (4 cups) heavy cream
    \item 2 quarts chicken broth
    \item 4 bay leaves
    \item Salt and black pepper to taste (maybe \( \frac{1}{2} \) to 1 teaspoon of each)
    \item 3 heads of broccoli, cut into small florets
    \item 12 grams sodium citrate (optional)
    \item 20 ounces medium sharp cheddar cheese, shredded
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Stock pot
    \item Ladle
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Make the double recipe of white roux in the stock pot.
    \item As soon as the white roux has cooked for it's 5 minutes and has just begun to change color, add in 32 ounces (4 cups) heavy cream.
    \item Stir to combine for about 3 minutes, this will likely bubble and fizzle for a second.
    \item Add 4 bay leaves and salt and pepper to taste.
    \item Add 3 heads of broccoli florets.
    \item Allow soup to come to a slow simmer over medium-low heat.
    \item Stir soup occasionally for the next 20-25 minutes, until broccoli is nearly as soft as you want it.
    \item Add in 12 grams sodium citrate and stir to combine.
    \item Add 20 ounces shredded medium cheddar and stir to combine.
    \item At this point the soup should be delicious.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is my own recipe, but everything except the sodium citrate is pretty standard.
    \item This recipe can be cut in half, except the sodium citrate should probably only be recuded to about 10 grams.
    \item The sodium citrate acts as an emulsifer with the cheese, which helps the soup not seperate on re-heating. Makes the leftovers nicer.
    \item You could add well-boiled potatoes or bits of carrots, they are delicious in this.
    \item Some people prefer flecks of broccoli, or even use blender to turn it all into tiny green specks. I don't care for that as much. Do what you want.
    \item Some people use velveeta for this, I find a good cheddar melts just fine, and tastes better.
\end{itemize}
\end{multicols}
\clearpage