\section{Caldo De Res}
\label{caldoDeRes}
\setcounter{secnumdepth}{0}
Time: 3 hours (20 minutes prep, 2 hours 40 minutes cooking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 680 grams beef (stew beef works)
    \item 450 grams beef leg shank
    \item 1900 grams (\( \frac{1}{2} \) gallon) water
    \item \( \frac{1}{2} \) sweet onion, chopped
    \item \( \frac{1}{2} \) Tablespoon kosher salt
    \item 1 \( \frac{1}{2} \) Tablespoons Better Than Bullion (beef)
    \item 1 bay leaf
    \item 2 Tablespoons (1 recipe) of \nameref{texMexHolyTrinity}
    \item 1 ear of sweet yellow corn, sliced into \( \frac{1}{2} \) inch rounds
    \item \( \frac{1}{2} \) zucchini, cut to 1 inch rounds
    \item \( \frac{1}{2} \) potato, cut to \( \frac{1}{2} \) inch pieces
    \item \( \frac{1}{2} \) choyote squash, chopped
    \item 1 cup celery, chopped
    \item 1 cup carrots, chopped
    \item 1 cup cabbage, chopped
    \item 1 \( \frac{1}{2} \) Tablespoons tomato sauce
    \item chopped mint for serving
    \item chopped cilantro for serving
    \item lime wedges for serving
    \item hot \nameref{tortillas} for serving
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Stock pot
    \item Cutting board
    \item large knife
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Place 680 grams stew beef, 450 grams beef leg shank, \( \frac{1}{2} \) gallon water, \( \frac{1}{2} \) sweet onion, 1 \( \frac{1}{2} \) Tablespoons Better Than Bullion, \( \frac{1}{2} \) Tablespoon kosher salt, and 1 bay leaf in the stock pot.
    \item Bring water to a boil over high heat.
    \item Redice heat, cover, and simmer for 2 hours, until beef is tender.
    \item Add 2 Tablespoons Tex Mex Holy Trinity, corn, potatoes, chayote, celery, carrots, cabbage, and tomato sauce to soup.
    \item Simmer for 15 minutes, until potatoes are tender.
    \item Set off the heat for 15 minutes to allow the soup to cool slightly and the flavors to marry a bit.
    \item Serve with mint, cilantro, lime wedges (squirted in), and tortillas.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Based on Sylvia Casares' recipe, as seen in The Enchilada Queen Cookbook (and more than 20 years living on the border).
    \begin{itemize}
        \item The main difference is I leave out sweet potatoes, and make this in a much smaller quantity.
        \item I also cook by weight for the meats.
    \end{itemize}
    \item I've never weighed the vegetables and just eyeball them. This is a very vegetable heavy soup.
    \item This soup was super common growing up in South Texas. My family didn't make it (they were rather white, and from West Texas originally), but all the Tex-Mex restaurants had it.
    \item TODO: Try browning the meat first before boiling. While nottraditional, I think it would add a lot more beefy-flavor. Might could even reduce the beef base then.
\end{itemize}
\end{multicols}
\clearpage