\section{Alfredo Sauce}
\label{alfredoSauce}
\setcounter{secnumdepth}{0}
Time: 20 minutes (5 minute prep, 15 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 1 pound Peeled shrimp or chicken breast
    \item Salt and pepper to taste
    \item Garlic powder
    \item Butter or olive oil to saute
    \item \( \frac{1}{2} \) cup butter
    \item 2 cup heavy whipping cream (higher fat content is better)
    \item 3 cloves garlic, crushed or minced
    \item 3 cups fresh-grated parmigiano reggiano
    \item \( \frac{1}{4} \) cup fresh chopped oregano, parsley, or marjoram
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Skillet
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Add salt, pepper, and garlic powder to 1 pound shrimp or chicken
    \item Saute shrimp in butter. Use olive oil for chicken.
    \item Set aside protein.
    \item In a skillet or saucepan, melt \( \frac{1}{2} \) cup butter at medium-low heat.
    \item Add 2 cups heavy cream, and simmer for 5 minutes while stirring.
    \item Add 3 cloves minced garlic to sauce, stir briefly.
    \item Add 3 cups grated cheese, stir cheese into sauce until the mixture is smooth.
    \item Mix in \( \frac{1}{4} \) cup oregano (or other green).
    \item Serve over protein source, usually on pasta (fettucini)

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item I tend to use really good heavy cream and actual parmigiano reggiano, as opposed to the faux American Parmasean Cheese. The taste of the sauce really benefits from good ingredients.
\end{itemize}
\end{multicols}
\clearpage