\section{Pesto}
\label{pesto}
\setcounter{secnumdepth}{0}
Time: 10 minutes
Serves: 2 cups (about 4 people)

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 ounces pine nuts
    \item 1 \( \frac{1}{2} \) ounces parmigiano reggiano, grated
    \item 1 \( \frac{1}{2} \) ounces pecorino romano, grated
    \item \( \frac{1}{2} \) teaspoon coarse salt
    \item 2 cloves garlic, chopped
    \item \( \frac{1}{2} \) ounce butter, in 2-3 pieces
    \item 6 ounces basil
    \item Generous \( \frac{1}{2} \) cup olive oil
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Baking sheet
    \item Food processor (or morter/pestle)
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Pre-heat oven to 350F.
    \item Spread pine nuts across baking sheet.
    \item Bake pine nuts in oven for about 2 minutes one side, then 1 minute on the other.
    \item Pine nuts should be just starting to brown a tiny amount.
    \item Pour pine nuts into bowl of food processor.
    \item Allow pine nuts to cool before using.
    \item Add 1 \( \frac{1}{2} \) ounces grated parmigiano reggiano and 1 \( \frac{1}{2} \) ounces grated pecorino romano to processor.
    \item Add \( \frac{1}{2} \) teaspoon coarse salt.
    \item Add 2 cloves roughly chopped garlic.
    \item Add \( \frac{1}{2} \) ounces butter.
    \item Pulse food processor until ingredients are just combined.
    \item Add leaves from 6 ounces of basil
    \item If all basil doesn't fit, add most of it, pule for a few second, then finish adding the rest.
    \item Once all basil is in the bowl, pusle for a couple of seconds at a time to combine all ingredients.
    \item Add about half the oil and pulse to combine.
    \item Add in the rest of the oil in a drizzle as the machine processes.
    \item Add oil until the pesto is at the desired consistency (slightly thicker than when used in pasta, normally).
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is my own pesto recipe, but it is a very standard recipe.
    \item While I don't see pecorino used as often in American pesto's, I consider it all but required. It's saltier than parmigiano reggiano.
    \item Adding this to most any sandwich or pasta is delicious. See \nameref{pestoAllaGenovese} for the standard technique for adding pesto sauce to pasta.
\end{itemize}
\end{multicols}
\clearpage