\section{Boiled Crawfish}
\label{boiledCrawfish}
\setcounter{secnumdepth}{0}
Time: 20 minutes (5 minutes prep, 15 minutes cooking)
Serves: 2

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item Enough water to cover food (probably about 6 quarts)
    \item 5 pounds live (ideally Louisiana) crawfish and/or blue crabs
    \item 1 pound small red potatoes, whole
    \item 2 ears of corn, shucked and cut in half
    \item 1 cups Crab Boil Spice Mixture (see \nameref{crabBoilSpiceMixture}) or 1 bottle of Zatarain's Crab Boil
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item 1 really large pot
    \item Slotted Spoon
    \item Second large pot, if using spice mixture versus crab boil liquid
    \item Strainer, if using spice mixture versus crab boil liquid
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Place 6 quarts of water (enough to cover the food) in the large stock pot.
    \item Dump spice mixture into water, and let water come to a hard boil.
    \item Place 1 pound potatoes and 2 ears of corn into the liquid. Allow to boil for about 10 minutes.
    \item Add seafood to the water.
    \item Allow crawfish to boil for about 8 minutes.
    \item Turn off heat, and allow crawfish and vegetables to soak for another 6 minutes.
    \item Either strain the food or pull it out with a slotted spoon.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is mostly my own recipe. While I've not yet tried a really large boil on my own (only ever been a guest), there is a recipe for 20 people in Acadiana Profile's Cajun Cooking, Part 1, page 191.
\end{itemize}
\end{multicols}
\clearpage