\section{Egg Noodles}
\label{eggNoodles}
\setcounter{secnumdepth}{0}
Time: 2 hours (1 \( \frac{3}{4} \) hours prepping, 2 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 10 \( \frac{1}{2} \) ounces of all purpose flour
    \item \( \frac{1}{2} \) teaspoon salt
    \item 3 eggs
    \item 3 quarts water
    \item 1 teaspoon salt
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Counter top
    \item Fork
    \item Rolling pin
    \item Sharp knife
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Sift the flour and salt together with a fork.
    \item Make a deep and wide well in the middle of the flour on a counter top.
    \item Place all three eggs in the well in the flour.
    \item Slowly mix the flour into the eggs to form a sticky dough. You may not use all the flour.
    \item Stop mixing once you have a somewhat sticky dough, and begin to knead it on a flour-covered counter top.
    \item Knead the dough until it is fairly smooth, but don't over work it or you won't be able to roll it flat enough.
    \item Allow the dough to rest under a moist towel at room temperature for at least 30 minutes.
    \item Cut the dough into 4 equal parts, leaving the other three under the towel.
    \item Roll out the dough into a rough rectangle, until it is very flat (slightly thinner than a normal noodle, as they will puff a tad while cooking).
    \item Cut the dough into strips (or whatever shape you want) about \( \frac{1}{4} \) inch wide, and 10 inches long.
    \item Place the sliced noodles under the towel as you work with each piece of dough.
    \item Repeat with the other three pieces of dough.
    \item Cook the noodles in about 2-3 quarts boiling water with 1 teaspoon salt mixed in, for about 1-2 minutes, until al dente.
    \item Remove the pasta from the boiling water.
    \item Eat with a sauce of your choice.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is a standard egg noodle recipe. While I have it in ounces, a common ratio is 100 grams of flour to each egg (ends up being about 10.5 ounces of flour for 3 eggs).
    \item While many people recommend a pasta roller and maybe cutter, I don't have one, so I've not really tried any.
    \item Pasta can be dried for storage and later use. I've not done that yet.
    \item Make sure that your surface and rolling pin stay lightly floured, in order to prevent sticking.
\end{itemize}
\end{multicols}
\clearpage