\section{Grilled Cheese Sandwich}
\label{grilledCheeseSandwich}
\setcounter{secnumdepth}{0}
Time: 30 minutes (5 minutes prep, 25 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 8 slices of good bread
    \item 8 \( \frac{1}{3} \) inch slices of good cheese (about \( \frac{1}{2} \) to \( \frac{3}{4} \) ounces per slice)
    \item 4 Tablespoons of butter
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Skillet
    \item Spatula
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Set the butter out to get near room temperature.
    \item Spread butter on each slice of bread.
    \item Heat a skillet to medium heat.
    \item Place \( \frac{1}{4} \) Tablespoon of butter in the skillet and allow it to melt.
    \item Place a piece of bread, butter-side down, in the skillet, then cover with cheese, then top with another piece of bread, butter-side up.
    \item Allow to grill at medium heat for about 5-7 minutes, until cheese is gooey and bread is browned.
    \item Flip the sandwich and allow to cook for another 5 minutes until the top bread is browned.
    \item Remove from the skillet, and repeat the above steps for each sandwich.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Recipe is my own, but it's a very typical recipe.
    \item I highly recommend using a really good bread, such as \nameref{whiteBread}, a good sourdough, or a nice Italian loaf. Good bread and cheese make all the difference in this.
    \item For cheeses, I typically use colby jack or provolone.
\end{itemize}
\end{multicols}
\clearpage