\section{Meatloaf}
\label{Meatloaf}
\setcounter{secnumdepth}{0}
Time: 1 hour 45 minutes (15 minutes prep, 1 hour and 25 minutes cooking, 10 minutes resting)
Serves: 6

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item \( \frac{1}{2} \) ounces butter
    \item 4 ounces sweet onion, diced
    \item 2 cloves garlic, minced
    \item 32 ounces ground beef (85\% lean)
    \item 3 \( \frac{1}{2} \) ounces bread crumbs
    \item 8 ounces (1 cup) milk
    \item 1 egg
    \item 1 Tablespoon worcestershire sauce
    \item 2 teaspoons dried oregano
    \item 2 teaspoons kosher salt
    \item \( \frac{1}{2} \) cup ketchup
    \item 2 Tablespoons dijon mustard
    \item 1 Tablespoon brown sugar
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Small saute pan, skillet, or sauce pan
    \item large mixing bowl
    \item Small bowl
    \item Cookie sheet
    \item Aluminum foil
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Pre-heat oven to 350F.
    \item Melt \( \frac{1}{2} \) ounces butter over medium heat in a small saute pan.
    \item Cook onions in butter until slightly browned while keeping them moving. About 10 minutes.
    \item Add 2 diced garlic cloves and cook while stirring for about 1 minute.
    \item Remove from heat.
    \item Place 32 ounces ground beef, 3 \( \frac{1}{2} \) ounces bread crumbs, 8 ounces of milk (poured over the bread crumbs), 1 egg, 1 Tablespoon worcestershire sauce, 2 teaspoons dried oregano, and 2 teaspoons kosher salt in a large mixing bowl.
    \item Add in the onions and garlic.
    \item Mix by hand just until combined.
    \item Cover a cookie sheet in foil.
    \item Shape meat into a loaf shape, about twice as long as it is wide.
    \item Bake in an oven for about 40 minutes.
    \item While baking, mix \( \frac{1}{2} \) cup ketchup, 2 Tablespoons dijon mustard, and 1 Tablespoon brown sugar in a small bowl.
    \item Once you have baked for 40 minutes, brush the sauce onto the top of the loaf.
    \item Continue baking until the internal temperature at the middle of the loaf reaches 160F (about 30 minutes).
    \item Remive from the oven and let rest at least 10 minutes before slicing.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Recipe is my own, but fairly normal stuff.
    \item Do not cook in a loaf pan. The sides seem to trap steam, makes the whole thing tougher in the end.
    \item You can just use ketchup as a sauce, but the mustard flavor is delicious.
\end{itemize}
\end{multicols}
\clearpage