\section{Pierogi Fillings}
\label{pierogiFillings}
\setcounter{secnumdepth}{0}
Time: Varies
Serves: 1 pierogi recipe

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item Potato and Cheese
    \begin{itemize}
        \item 1 potato (about 12 ounces), peeled and chopped
        \item 3 ounces cheese, shredded
        \item Salt and pepper to taste
    \end{itemize}
    \item Sauerkraut (TO TRY)
    \begin{itemize}
        \item 3 cups \nameref{sauerkraut}
        \item 2 Tablespoons sour cream
        \item 2 ounces onion, chopped
        \item 4 Tablespoons fat for cooking (bacon fat, lard, or butter)
        \item salt and pepper to taste
    \end{itemize}
    \item Blueberries (TO TRY)
    \begin{itemize}
        \item 16 ounces blueberries
    \end{itemize}
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Varies, do what you feel works.
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Potato and Cheese
    \begin{itemize}
        \item Boil potato pieces in water until tender.
        \item Drain potatoes.
        \item Add cheese, salt, and pepper.
        \item Stir until well combined.
        \item Use in savory \nameref{pierogi}
    \end{itemize}
    \item Sauerkraut (TO TRY)
    \begin{itemize}
        \item Rince the sauerkraut in warm water and squeeze dry.
        \item Chop sauerkraut finely.
        \item Cook the onion in the fat of your choice until slightly transparent.
        \item Add the sour cream and sauerkraut to the onion.
        \item Salt and pepper to taste.
        \item Cook all ingredients for about 10-15 minutes, until tender and the flavors are blended.
        \item Allow to cool in the fridge before use in a savory \nameref{pierogi}
    \end{itemize}
    \item Blueberries (TO TRY)
    \begin{itemize}
        \item Place a tiny handful of blueberries into each dumpling.
        \item for use in sweet \nameref{pierogi}
    \end{itemize}
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Potato and cheese filling is my own, but it's really rather standard and common.
    \item Sauerkraut is taken from Genius Kitchen, as seen here: \url{https://www.geniuskitchen.com/recipe/homemade-sauerkraut-pierogies-perogies-old-fashioned-recipe-66653}
    \item BLueberry recipe is pretty standard for sweet pierogi.
\end{itemize}
\end{multicols}
\clearpage