\section{Quiche}
\label{quiche}
\setcounter{secnumdepth}{0}
Time: 1 \( \frac{1}{2} \) hours (20 minutes prep, 1+ hours baking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 8 eggs
    \item \( \frac{1}{4} \) cup milk
    \item \( \frac{1}{2} \) lb. bacon
    \item 12 ounces frozen broccoli
    \item 1 cup fresh baby spinach
    \item \( \frac{1}{2} \) tbsp olive oil
    \item Salt and pepper to taste
    \item Pie crust (see \nameref{pieCrust} recipe)
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Mixer or mixing bowl and whisk
    \item Pie dish
    \item Butter knife
    \item Sharp knife and spatula to cut and serve
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Make the pie crust per the standard recipe. As the dough rests in the fridge, do the following steps.
    \item Fry \( \frac{1}{2} \) lb. bacon in pan using normal method.
    \item Remove bacon from heat and grease.
    \item Crumble bacon.
    \item Place 1 cup fresh spinach in skillet with olive oil, low-medium heat.
    \item Add salt to taste, cook spinach till it’s soft.
    \item Chop cooked spinach.
    \item Place 8 eggs and whisk till they have some air in them.
    \item Add \( \frac{1}{4} \) cup milk to eggs, mix in.
    \item Add all frozen broccoli, spinach, and bacon crumbs to egg mixture.
    \item Finish pie crust and place in pie dish.
    \item Place filling in pie crust.
    \item Bake at 375 for 50-60 minutes, until eggs are set (shake pan to check setness).
    \item When done, poke the pie pan with a butter knife to check final setness.
    \item Let cool for 5 minutes, serve.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Adding other vegetables can be done, such as grilled bell peppers or onion, however more veggies is more moisture, which can make it take longer to set, which browns the crust more. Be wary of adding too many veggies.
    \begin{itemize}
        \item Might can offset this by thawing the broccoli more, need to test.
    \end{itemize}
\end{itemize}
\end{multicols}
\clearpage