\section{Slow Cooker Boston Butt}
\label{slowCookerBostonButt}
\setcounter{secnumdepth}{0}
Time: 7 hours (20 minutes prep, 6 \( \frac{1}{2} \) hours inactive cooking)
Serves: 6

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 1 pound carrot sticks (or carrots, cut into small pieces)
    \item \( \frac{1}{2} \) cup of water
    \item 3-4 pound boneless Boston butt, cut into 8 pieces (they will be rather large)
    \item Salt, pepper, and garlic powder to taste
    \item 1 tablespoon ground mustard seed
    \item splash of white vinegar
    \item \( \frac{1}{2} \) cup of butter (1 stick)
    \item 1 teaspoon garlic powder
    \item \( \frac{1}{2} \) teaspoon onion powder
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Slow cooker
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Place 1 pound of carrot sticks in slow cooker.
    \item Take your roast, add salt, pepper, garlic powder, and 1 tablespoon ground mustard seed to every side.
    \item Place roast on top of carrots.
    \item Place \( \frac{1}{2} \) cup butter (1 stick) on top of roast.
    \item Add 1 teaspoon garlic powder and\( \frac{1}{2} \) teaspoon onion powder on top of butter.
    \item Turn heat to low, and cook for about 6 or 6 \( \frac{1}{2} \) hours, turning the meat chunks once during cooking.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Recipe is based on my \nameref{slowCookerPotRoast} recipe. I do not like it as much, but when I make \nameref{slowCookerPorkCarnitas} I tend to by a 7-8 pound roast, cut it in half, and make both recipes.
\end{itemize}
\end{multicols}
\clearpage