\section{Spaghetti Alle Vongole In Bianco}
\label{spaghettiAlleVongoleInBianco}
\setcounter{secnumdepth}{0}
Time: 2 hour 30 minutes (30 minutes prep, 1 hour sitting, 30 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item Water to fill a large bowl
    \item Salt to make the water salty
    \item 1360 grams of clams (live clams, or so help me)
    \item 40 grams olive oil, more as needed
    \item 3 cloves garlic, peeled and sliced very thin
    \item Pinch of red pepper flakes (optional, but highly recommended)
    \item 120 grams dry, white, italian wine
    \item 450 grams spaghetti
    \item Water to boil
    \item Salt for boiling water
    \item 15 grams butter
    \item Fresh italian parsely, minced
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Large mixing bowl
    \item Large skillet
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Fill large bowl with cold water and stir in some salt to make the water salty.
    \item Add clams into the salt water and let sit for 30 minutes.
    \item Lift clams from water and discard water. If there is sant in the bowl, rinse and repeat the preceeding steps until there is no sand (usually 2-3 times).
    \item Discard any clams that are wide open and refuse to close when prodded. They have died and will not taste good.
    \item In the skillet, combine 40 grams olive oil, 3 cloves sliced garlic, and a pinch of red pepper flakes.
    \item Cook over medium heat until garlic turns lightly golden colored, about 5 minutes.
    \item Add 120 grams white wine and clams.
    \item Cover and bring heat to high.
    \item Cook and check under the lid every 30 seconds or so. As soon as any clam opens, transfer it to a clean mixing bowl. Continue until all clams have opened.
    \item Remove skillet from heat.
    \item Save a few clams per plate in the shells, but remove the meat from the rest of the clams.
    \item Cook 450 grams of spaghetti in boiling salt water until just shy of al dente (about 6 minutes for dry pasta).
    \item Place pasta in skillet with wine sauce.
    \item Add a few Tablespoons of pasta water to the sauce.
    \item Cook over high heat, stirring and tossing until sauce reduces and forms a creamy coating on the noodles.
    \item Add 15 grams butter and clam meat to pasta, toss to combine.
    \item Remove from heat.
    \item Salt and pepper to taste.
    \item Top with fresh parsely and olive oil, serve hot.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Based on Daniel Gritzer's recipe, as seen here: \url{https://www.seriouseats.com/recipes/2016/02/spaghetti-pasta-alle-vongole-clams-recipe.html}
    \begin{itemize}
        \item Main differences are everything is by weight, a few added notes on wine and clams.
    \end{itemize}
    \item "In Bianco" means this is the white version, using the olive oil sauce with white wine. A common variation is "in rosso", red, using tomatoes and basil.
    \item This is a dish from Neopolitan cuisine, near as I know. Not sure anyone knows who made it first. The white version is very simple, and is common in any part of Italy with seafood.
    \item I've seen this served with cheese (such as parmigiano reggiano), but I prefer it without. The clams and olive oil are subtly flavored and easily over powered.
\end{itemize}
\end{multicols}
\clearpage