\section{Champignons Sautés Au Beurre}
\label{champignonsSautesAuBeurre}
\setcounter{secnumdepth}{0}
Time: 1 hour (10 minutes prep, 50 minutes baking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 Tablespoons butter
    \item 1 tablespoon olive oil
    \item \( \frac{1}{2} \) pound fresh mushrooms, washed, quartered, and dried
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Skillet
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Ensure the mushroom quarters are well dried to ensure proper cooking without steaming.
    \item Place the skillet over high heat.
    \item Add 2 Tablespoons butter and 1 tablespoon olive oil.
    \item Allow fats to heat. Make sure the butter gets past the foamy stage, but not quite smoking.
    \item Add mushroom quarters, not crowded (likely need 2 or 3 batches).
    \item Keep the pan shaking, the mushrooms should absorb the fats.
    \item Keep the mushrooms moving for 4 or 5 minutes, until they start to release the fats back into the skillet.
    \item remove the mushrooms when they are lightly browned. You want them to retain some good texture.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is based on the recipe of Julia Child, Simone Beck, and Louisette Bertholle, as seen in Mastering the Art of French Cooking, Volume 1, page 513.
    \begin{itemize}
        \item The book details other methods to prepare these, I highly recommend reading it.
    \end{itemize}
    \item While I normally place these on top of \nameref{boeufBourguignon}, they can also be eaten as a side or combined with other vegetables.
\end{itemize}
\end{multicols}
\clearpage