\section{Collard Greens}
\label{collardGreens}
\setcounter{secnumdepth}{0}
Time: 3 hours (30 minutes prep, 2 and \( \frac{1}{2} \) hours cooking)
Serves: 6

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item \( \frac{1}{2} \) pound of bacon, about 4 thick cut slices
    \item \( \frac{1}{2} \) sweet onion, chopped
    \item \( \frac{1}{2} \) pound tasso ham (see \nameref(tassoHam)), diced
    \item 4 cloves garlic, minced
    \item 1 quart chicken broth
    \item 1 pound collard greens, stems trimmed out
    \item 2 tablespoons apple cider vinegar
    \item \( \frac{1}{2} \) tablespoon sugar
    \item \( \frac{1}{2} \) teaspoon salt
    \item \( \frac{1}{4} \) teaspoon black pepper
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Skillet
    \item 4 Quart stock pot
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Cook bacon in skillet, at medium heat until somewhat crispy.
    \item Set bacon aside, move bacon fat to stock pot.
    \item Add \( \frac{1}{2} \) chopped onion at medium heat and saute for 5-10 minutes, until slightly cooked.
    \item Add diced \( \frac{1}{2} \) pound tasso ham and 4 minced cloves garlic. Cook for 2 minutes.
    \item Add 1 quart broth, 1 pound of collard greens, 2 tablespoons apple cider vinegar, \( \frac{1}{2} \) tablespoon sugar, \( \frac{1}{2} \) teaspoon salt, and \( \frac{1}{4} \) teaspoon black pepper.
    \item Stir all ingredients together and lower heat to low.
    \item Cook at low heat for about 2 hours, until leaves are tender.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item the tasso ham tends to make this pretty spicy, use regular smoked ham instead if you don't want the spice, or want a more traditional flavor.
\end{itemize}
\end{multicols}
\clearpage