\section{Frijoles Refritos}
\label{frijolesRefritos}
\setcounter{secnumdepth}{0}
Time: 10 minutes (10 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 3 Tablespoons lard
    \item 2 ounces (about \( \frac{1}{4} \) of a) sweet onion, diced
    \item 2 cups cooked beans (such as \nameref{pentoBeans})
    \item About \( \frac{1}{2} \) cup of the bean broth (fill measuring cup with beans, then with broth to 1 cup line)
    \item \( \frac{1}{2} \) teaspoon salt
    \item (optionally) queso cotija and tortillas for serving
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Skillet
    \item Stiff plastic spatula (or a potato masher, if you have one)
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Heat the lard in the skillet over meadium heat.
    \item Cook the onion until slightly transparent, about 1 minute.
    \item Add 2 cups of beans and the bean broth, as well as \( \frac{1}{2} \) teaspoon salt.
    \item Crush the beans with your spatula until you get the consistency desired.
    \item Fry them for about 5 minutes, they will get thicker and lose liquid as this goes on.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is based on the "Mexican Authentic Recipes", as seen here: \url{http://www.mexican-authentic-recipes.com/antojitos-frijoles_refritos.html}
    \begin{itemize}
        \item Main difference is slight portion differences, and I don't eat these with totopos.
    \end{itemize}
    \item These are a great side for Mexican and Tex-Mex food.
    \item These are also an integral part of \nameref{botanas}, both as a component and a side.
\end{itemize}
\end{multicols}
\clearpage