\section{Green Bean Casserole}
\label{greenBeanCasserole}
\setcounter{secnumdepth}{0}
Time: 1 hour 30 minutes (30 minutes prep, 1 hour cooking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 3 quarts of water
    \item 1 \( \frac{1}{4} \) ounces (about \( \frac{1}{4} \) cup) all purpose flour
    \item 2 Tablespoons panko bread crumbs
    \item 1 teaspoon salt
    \item 2 medium yellow onions, sliced thinly into rings
    \item Non-stick cooking spray
    \item 1 recipe of \nameref{creamOfMushroomSoup}
    \item 24 ounces green beans (frozen or fresh, but not canned)
    \item 1 \( \frac{1}{2} \) Tablespoon salt
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Stockpot
    \item Medium mixing bowl
    \item Cookie sheet
    \item 9x13 Baking dish
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Preheat oven to 400F.
    \item Bring 3 quarts of water and 1 \( \frac{1}{2} \) Tablespoon salt to a boil in a stock pot.
    \item Combine 1 \( \frac{1}{4} \) ounces all purpose flour, 2 Tablespoons panko bread crumbs, and 1 teaspoon salt in a medium mixing bowl and whisk thouroughly.
    \item Toss the sliced onion rings in the flour mixture.
    \item Allow onions to rest for about 5 minutes.
    \item Spray a cookie sheet with non-stick spray.
    \item Evenly spread onion across cookie sheet.
    \item Bake onion for about 30 minutes, turning and moving them every 5 minutes, until well browned.
    \item Remove onions and allow to cool.
    \item If you have not yet, make a recipe of \nameref{creamOfMushroomSoup}.
    \item While the onions are cooking, blanch 24 ounces of green beans in 3 quarts of boiling water.
    \item Drain the greenbeans, and rinse with cold water to prevent over-cooking.
    \item Coat 9x13 baking dish with non-stick spray.
    \item In the baking dish, combine greenbeans with cream of mushroom soup.
    \item Top with onions.
    \item Bake at 375F for about 15-20 minutes, until bubbly.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is mostly Alton Brown's recipe.
    \begin{itemize}
        \item The main difference is I use my standard cream of mushroom soup, rather than his.
    \end{itemize}
    \item This is immensely better than using canned soup and store-bought fried onions.
    \item I tend to serve this at Thanksgiving.
\end{itemize}
\end{multicols}
\clearpage