\section{Mizeria}
\label{mizeria}
\setcounter{secnumdepth}{0}
Time: 50 minutes (5 minutes prep, 45 minutes resting)
Serves: 6

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 cucumbers (about 300 grams), peeled and sliced into very thin rounds
    \item Kosher salt to taste
    \item 28 grams white vinegar (2 Tablespoons)
    \item 150 grams (about \( \frac{1}{2} \) cup) full fat sour cream
    \item 2 Tablespoons fresh dill, chopped
    \item 2 Tablespoons chives, chopped
    \item 1 teaspoon granulated white sugar
    \item Black pepper to taste
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Baking sheet
    \item Cooling rack
    \item Large mixing bowl
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Lay 300 grams thin cucumber rounds in a single layer on a cooling rack over a baking sheet.
    \item Sprinkle salt over all slices.
    \item Let the cucumbers sit for 20 minutes to draw out some water while you prepare the dill sauce.
    \item Combine 28 grams white vinegar, 150 grams sour cream, 2 Tablespoons chopped fresh dill, 2 Tablespoons chopped chives, 1 teaspoon granulated sugar, and black pepper to taste in a mixing bowl.
    \item Dab water off of the cucumbers after 20 minutes.
    \item Toss the cucumbers in the dill sauce.
    \item Chill in the fridge.
    \item Serve cold.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item I got ideas from the mizeria recipe here: \url{https://www.kwestiasmaku.com/przepis/mizeria}
    \begin{itemize}
        \item Main differences are vinegar instead of lemon juice, pepper after the salting, and a bit of sugar to cut the bite.
    \end{itemize}
    \item I should try lemon juice at some point instead, but I really like the almost pickle-like bite of the vinegar on fresh cucumbers.
    \item This holds pretty well through the following day covered in the fridge, but the cucumbers get too soft after a few days.
\end{itemize}
\end{multicols}
\clearpage