\section{Oignons Glacés À Brun}
\label{oignonsGlacesABrun}
\setcounter{secnumdepth}{0}
Time: 1 hour (10 minutes prep, 50 minutes baking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 cups water
    \item 20-25 small white onions
    \item 1 \( \frac{1}{2} \) Tablespoons butter
    \item 1 \( \frac{1}{2} \) Tablespoons olive oil
    \item \( \frac{1}{2} \) cup red wine or beef stock
    \item 4 parsley sprigs
    \item \( \frac{1}{2} \) bay leaf
    \item \( \frac{1}{4} \) teaspoon thyme
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Sauce pan
    \item Skillet
    \item Small baking dish (big enough to hold all onions in one layer)
    \item Cheesecloth
    \item Butcher twine
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Get water to boiling in sauce pan.
    \item Place onions in boiling water for 20 seconds.
    \item Remove onions from heat.
    \item Snip the very tip off of each side of each onion.
    \item Remove the outer skin from each onion.
    \item Cut out the tiny hard rooty side of the onion.
    \item Get 1 \( \frac{1}{2} \) Tablespoons butter and 1 \( \frac{1}{2} \) Tablespoons olive oil to bubbling in the skillet.
    \item Sauté the onions over medium heat, keep them constantly moving to brown them as evenly as possible.
    \item Place the onions and the fats into the small baking dish.
    \item Pour the liquid over the onions.
    \item Place 4 parsley sprigs, \( \frac{1}{2} \) bay leaf, and \( \frac{1}{4} \) teaspoon thyme into the cheesecloth and tie closed with butcher twine.
    \item Place herb bouqet in liquid.
    \item Set dish uncovered in in 350F oven (325F works too if you are making these with \nameref{boeufBourguignon}).
    \item Bake for about 25 minutes.
    \item Turn the onions over once.
    \item Bake for another 25 minutes.
    \item The onions should be tender but retain their shape.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is based on the recipe of Julia Child, Simone Beck, and Louisette Bertholle, as seen in Mastering the Art of French Cooking, Volume 1, page 483.
    \begin{itemize}
        \item The book details other methods to prepare these, I highly recommend reading it.
    \end{itemize}
    \item Translates to "Brown-Braised Onions".
    \item While I normally place these on top of \nameref{boeufBourguignon}, they can also be rolled in 1 Tablespoon butter with a Tablespoon minced parsely. This is called "Petits Oignong Persillés", or "parslied Onions".
\end{itemize}
\end{multicols}
\clearpage