\section{Stovetop Mac and Cheese}
\label{stovetopMacAndCheese}
\setcounter{secnumdepth}{0}
Time: 1 hour (15 minutes prep, 45 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 1 pound elbow macaroni (or shells... love me some shells)
    \item 1 tablespoon olive oil
    \item 1 teaspoon salt
    \item \( \frac{1}{4} \) cup butter
    \item \( \frac{1}{4} \) cup flour
    \item \( \frac{1}{2} \) teaspoon table salt
    \item \( \frac{1}{8} \) teaspoon black pepper
    \item 2 cups milk
    \item 2 cups cheese, shredded (chedder, colby... as long as it melts)
    \item 4 slices bacon (optional)
    \item 16 ounces broccoli (optional)
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Large pan
    \item Medium sauce pan
    \item Skillet (optional, for bacon)
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item If you want to add bacon, cook it per the \nameref{crispyBacon} recipe.
    \item Combine about 4 quarts of water, 1 tablespoon olive oil, and 1 teaspoon salt.
    \item Bring water to a good boil over High heat.
    \item While cooking bacon, cook the 1 pound of macaroni to just before al dente (usually about 5-6 minutes) in the boiling water.
    \item As the macaroni is cooking, melt the \( \frac{1}{4} \) cup butter at medium-low heat.
    \item Sprinkle in all of the \( \frac{1}{4} \) cup flour, and stir to combine.
    \item Keep cooking the flour and butter for 4-5 minutes to create a light roux. Do not stop stirring the roux for the entire 5 minutes.
    \item Stir \( \frac{1}{2} \) teaspoon salt and \( \frac{1}{8} \) teaspoon black pepper into the roux.
    \item Stir in the about \( \frac{1}{5} \) of the milk.
    \item Ensure the milk is is well mixed with the roux, and that no clumps remain.
    \item Continue to add in and fully combine milk \( \frac{1}{5} \) at a time until it is all combined.
    \item Add in cheese, about \( \frac{1}{5} \) at a time, ensuring it is fully melted before adding in the next \( \frac{1}{5} \) of cheese.
    \item Drain the macaroni of water.
    \item Add cheese sauce to the macaroni.
    \item (optional steps): Steam the broccoli and stir in with the cheese.
    \item (optional step) Chop the bacon into small pieces and stir in with the cheese.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Based on the Genius Kitchen recipe: \url{http://www.geniuskitchen.com/recipe/easy-stove-top-macaroni-cheese-60350}
    \begin{itemize}
        \item Main differences are more detail in making the roux.
        \item Addition of bacon and broccoli.
    \end{itemize}
    \item I usually either use chedder or colby jack, both are delicious.
    \item For noodles I actually prefer shells to traditional elbows. I find the cheese gets stuck inside the shells, and you get little cheesy pockets.
    \item I don't always add bacon or broccoli, but sometimes it's nice.
    \item You can add 1 pound of browned ground beef with broccoli to get something akin to an entree, if you prefer.
\end{itemize}
\end{multicols}
\clearpage