\section{Sweet Potato Casserole}
\label{sweetPotatoCasserole}
\setcounter{secnumdepth}{0}
Time: 55 minutes (10 minutes prep, 45 minutes cooking)
Serves: 8

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 48 ounces sweet potatoes, peeled and chopped
    \item 4 quarts water
    \item 2 Tb butter
    \item \( \frac{1}{4} \) cup milk
    \item \( \frac{1}{4} \) teaspoon cinnamon
    \item \( \frac{1}{4} \) teaspoon nutmeg
    \item \( \frac{1}{4} \) teaspoon grains of paradise (ground)
    \item \( \frac{1}{2} \) teasppon table salt
    \item 1 Tb butter for pan
    \item 4 Tb butter, softened for streusel
    \item 2 ounces (about \( \frac{1}{4} \) cups) brown sugar
    \item 1 \( \frac{1}{2} \) ounces (about \( \frac{1}{4} \) cup) all purpose flour
    \item \( \frac{1}{4} \) teaspoon cinnamon
    \item \( \frac{1}{4} \) teaspoon nutmeg
    \item \( \frac{1}{4} \) teaspoon grains of paradise (ground)
    \item 2 ounces (about \( \frac{1}{2} \) cup) chopped pecans
    \item 2 ounces (about 3 cups) mini marshmallows, divided
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Stock pot
    \item Medium mixing bowl
    \item 9x13 baking dish
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Place 48 ounces peeled and chopped sweet potatoes in a stock pot, and cover with water (about 4 quarts).
    \item Bring to a boil and cook until tender, about 6 minutes.
    \item Drain the water.
    \item Add 2 Tablespoons butter, \( \frac{1}{4} \) cup milk, \( \frac{1}{4} \) teaspoon cinnamon, \( \frac{1}{4} \) teaspoon nutmeg, \( \frac{1}{4} \) teaspoon grains of paradise, and \( \frac{1}{2} \) teasppon table salt.
    \item Mash the potatoes.
    \item Preheat oven to 375F.
    \item Spread 1 Tablespoon of butter to coat inside of 9x13 baking dish.
    \item Spread the mashed potatoes in the baking dish.
    \item Prepare the streusel by combining 4 Tablespoons softened butter, 2 ounces brown sugar, 1 \( \frac{1}{2} \) ounces all purpose flour, \( \frac{1}{4} \) teaspoon cinnamon, \( \frac{1}{4} \) teaspoon nutmeg, \( \frac{1}{4} \) teaspoon grains of paradise, and 2 ounces chopped pecans in a mixing bowl.
    \item Stir until combined.
    \item Sprinkle the top of the potatoes with streusel and marshmallows evenly.
    \item Bake until heated through, about 10 minutes.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is my own recipe.
    \item If you bake near the top heating element, the marshmallows will get slightly browned and delicious.
    \item I tend to serve these at Thanksgiving.
    \item The Grains of Paradise can be ommited if you can't find them, but I think they add a delicious spiced flavor to the dish. I highly recommend finding some of you can.
\end{itemize}
\end{multicols}
\clearpage