\section{White Rice}
\label{whiteRice}
\setcounter{secnumdepth}{0}
Time: 35 minutes (5 minutes prep, 30 minutes cooking)
Serves: 4

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 1 cup uncooked rice
    \item 2 cups water
    \item 1 Tablespoon vegetable oil
    \item 1 teaspoon salt
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Sauce pan with lid
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Mix 1 cup uncooked rice, 2 cups water, 1 tablespoon oil, and 1 teaspoon salt in the sauce pan.
    \item Bring water to a boil over high heat.
    \item As soon as the water is boiling, reduce heat to medium.
    \item As soon as the water is at the same level as the rice, reduce the heat to low and cover with lid.
    \item Allow the rice to cook covered for another 20 minutes.
    \item Remove from heat and allow the rice to sit for 5-10 minutes.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is the rice recipe as seen in Acadiana Profile’s Cajun Cooking: From the Kitchens of South Louisiana, Part 1, 1990.
    \begin{itemize}
        \item My only difference is I pretty much always use oil over butter.
    \end{itemize}
    \item If you need more rice at a time, just ensure that there is enough water to cover the rice by about one joint of your index finger. Increase oil and salt, but not proportionate to this recipe. Experiment for larger batches of rice.
\end{itemize}
\end{multicols}
\clearpage