\chapter{Barbecue and Other Meats}
\label{barbecueAndOtherMeats}
\setcounter{secnumdepth}{0}
\minitoc
Smoked and grilled meats deserved their own special chapter apart from Entrées, partly due to their very different preperations, and partly because these are the epitome of good food. Barbecue is my favorite food, pretty much period.

"Barbecue is meat, prepared in a very special way..." -Rhett \& Link

Barbecue is not a grill, smoker, nor is it a cookout. While often used as a verb, it is also not a verb. Barbecue is meat, made deliciously. While traditionally barbecue is meat that is smoked or grilled, and originates in either Northern Mexico or The South, I like to take the above, broad defenition. Meat, prepared in a very special way...

This means that, to me, technically fajitas, barbacoa, jerk chicken... all barbecue (including of course, more traditional barbecue, such as smoked brisket and pulled pork.)

The next thing that should be noted is that I'm from Texas. This means I prefer beef, slow smoked over oak or hickory, and covered in a dry rub. Sauce is not really necessary. Usually if I'm having people over to partake in my delicious meat, I will also prepare a sauce, but it's only to please other people. I don't really use it much myself (at least on brisket and beef ribs, pulled pork is another story entirely.) This is because in The South the only thing that MIGHT trump meat is good ol' hospitality.

One final note. Entire books can and have been written on barbecue. If you really want to produce top tier barbecue, you need more than can be placed in a two page recipe. You need to have some understanding if your heat source, wood source, smoke, evaporative cooling, bark formation, smoke absorption, spices, cuts of meat... it's really quite a list. While other books can definitely help you get started (and I highly recommend reading a full book on Barbecue, such as "Franklin Barbecue: A Meat-Smoking Manifesto" or "Smoke and Spice"), there is no substitute for getting out there on a smoker, and making delicious, smokey meat. Try to get at least a basic understanding, then just start making meat. Worse comes to worse, you have a semi-delicious not-yet-rendered piece of meat. That still sounds edible.

Get outside, chop some wood, tend a fire, and enjoy the flesh of that animal. It's life was taken for you, you should make sure it adds the maximum amount of enjoyment to yours.

I dedicate this chapter to Edgar Black Jr. of Black's barbecue, Francisco Saucedo and Brendan Lamb of La Barbecue, Ronnie Killen of Killen's barbecue, Tim McGuffin who made a brisket and shared it with me once, Aaron Franklin of Franklin Barbecue, and maybe most importantly, Leroy "Spooney" Kenter, Jr., formerly of Spooney's Bar B Que. All of whom I've eaten their barbecue, some of who I've shared laughs with, all of whom I look up to, and a couple of whom I'll miss, whether or not we met in person.

-Caleb
\clearpage

%\input{chapters/barbecueAndOtherMeats/cajunAndouille}
%\input{chapters/barbecueAndOtherMeats/bacon}
%\input{chapters/barbecueAndOtherMeats/beefFajita}
\input{chapters/barbecueAndOtherMeats/hamburgers}
\input{chapters/barbecueAndOtherMeats/smokedBeefPlateRibs}
\input{chapters/barbecueAndOtherMeats/smokedBrisket}
\input{chapters/barbecueAndOtherMeats/smokedPorkRibs}
%\input{chapters/barbecueAndOtherMeats/smokedSalmon}
%\input{chapters/barbecueAndOtherMeats/tasso}