\section{Hamburgers}
\label{hamburgers}
\setcounter{secnumdepth}{0}
Time: 45 minutes (30 minutes prep, 15 minutes cooking)
Serves: 6

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 pounds hamburger
    \item \( \frac{1}{4} \) cup vegetable oil
    \item Salt and black pepper to taste
    \item buns
    \item any other toppings you'd like (lettuce, tomato, bacon, cheese, etc.)
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Cookie sheet
    \item Grill
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Take your beef and split it into 6 equal parts (each about \( \frac{1}{3} \)) pound in size.)
    \item Allow patties to rest in the fridge for about 15 minutes to firm up a tad.
    \item Ensure you have a very hot fire under the grill.
    \item Form each portion into a very wide patty (it should be wider than the buns, as it will shrink a lot).
    \item Coat each patty in a very light coat of oil.
    \item Sprinkle salt and pepper on each patty, on all sides.
    \item Place each patty down on a hot part of the grill.
    \item Close the grill door and allow the patties to cook about 3-4 minutes.
    \item Open the grill and flip each patty.
    \item Close the grill and allow to cook for another 3-4 minutes.
    \item If you want to toast buns (which I recommend) lightly butter your buns and place them on the grill for about 1-2 minutes per side.
    \item While the buns are grilling, place cheese on each patty and cover the patties in a pan with foil to allow the cheese to melt.
    \item Build your burgers and enjoy.

\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item There is nothing fancy in this recipe. Salt, pepper, and oil to allow the seasoning to stick to the patty, and keep the patty from sticking to the grill.
    \item Do not put cheese on the patty in the grill, it will drip off and land all over your wood, which can be hard to clean.
    \item For toppings, I like to have iceberg lettuce, tomato, crispy bacon, avacado, grilled mushrooms, grilled onions, mayo, and mustard. Do what you like. This is America.
\end{itemize}
\end{multicols}
\clearpage