\section{Tortillas}
\label{tortillas}
\setcounter{secnumdepth}{0}
Time: 35 minutes (10 minutes prep, 25 minutes baking)
Serves: 12 tortillas

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 8 ounces masa de harina
    \item scant \( \frac{1}{2} \) teaspoon salt
    \item 11 ounces (generous 1 \( \frac{1}{4} \) cup) water (add more as needed)
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Mixing bowl
    \item Plastic wrap
    \item Heavy flat bottomed pot, rolling pin, or tortilla press
    \item Cast iron skillet

\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Place cast iron skillet over medium heat
    \item Combine 8 ounces masa de harina, scant \( \frac{1}{2} \) teaspoon salt, and 11 ounces water in a mixing bowl.
    \item Mix to combine, and work the dough for about 3-5 minutes.
    \item If dough is not coming together, add 1 Tablespoon of water and work further. Repeat until dough comes together.
    \item Split dough into 12 equal parts, each part being about a golf ball in size.
    \item Cover with a damp towl.
    \item Place a sheet of plastic wrap, about 9 inches by 9 inches on a flat surface.
    \item Place a dough ball in the middle of the plastic.
    \item Cover with the second sheet of plastic.
    \item Place a heavy, flat-bottomed pot on top of the dough ball and press down hard with your weight.
    \item Optionally, use a rolling ping or tortilla press instead.
    \item Place the flattened tortilla into the skillet.
    \item Cook for about 1 \( \frac{1}{2} \) to 2 minutes per side, until the side has just a touch of brown.
    \item Store in a thick kitchen towel while cooking to stay warm.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item This is a pretty standard recipe, except that I cook by weight and use a heavy pot to flatten tortillas.
    \item Using a rolling pin or press is the most common at-home method, but I find rolling pins make it hard to press evenly without a lot of practice, and I don't own a press.
    \item It's pretty easy to cook these in 3 or so skillets at once, so that they come out much sooner.
\end{itemize}
\end{multicols}
\clearpage