\section{White Bread}
\label{whiteBread}
\setcounter{secnumdepth}{0}
Time: 3 hours (30 minutes prep, 1+ hours inactive rising, 25 minutes baking)
Serves: 3 loaves (about 12 people)

\begin{multicols}{2}
\subsection*{Ingredients}
\begin{itemize}
    \item 2 tablespoons olive oil
    \item 2 tablespoons honey
    \item 2 teaspoons salt
    \item About 6 \( \frac{1}{2} \) cups bread flour (2 for starter, 3 for dough, 1 \( \frac{1}{2} \) for kneading)
    \item 2 cups warm water (115F)
    \item 2 tablespoons yeast
    \item Extra oil for greasing bread pans
\end{itemize}

\subsection*{Hardware}
\begin{itemize}
    \item Small bowl
    \item Large mixing bowl
    \item Silicon spatula
    \item Tea towel
    \item 3 bread pans
\end{itemize}
\clearpage

\subsection*{Instructions}
\begin{enumerate}
    \item Mix 2 tablespoons olive oil, 2 tablespoons honey, and 2 teaspoons salt in a small bowl.
    \item Heat water to just above 115F (about 120F or so), then mix with 2 cups of bread flour in a large mixing bowl.
    \item Add in olive oil/honey mixture, stir briefly.
    \item Add in yeast, stir to combine.
    \item Let this mixture sit until bubbly, about 10 minutes.
    \item Add in 3 cups of flour and mix until it becomes slightly hard to stir.
    \item Turn dough onto a floured surface, sprinkle some flour on top of the dough.
    \item Knead the dough, adding in flour fairly often as you do.
    \item Knead for about 8 minutes, until the texture is similar to that of an ear lobe.
    \item Clean out large mixing bowl, return dough to bowl, cover with a moist tea towel.
    \item Let dough sit at room temperature about 45 minutes, until doubled in size.
    \item Punch down dough in bowl, then turn out into lightly floured surface.
    \item Separate dough into 3 equal sized pieces.
    \item Lightly oil each pan, then place a piece of dough into each one.
    \item Cover the pans and let rise, about 20-30 minutes, until the pan is mostly full.
    \item Place each pan in the oven and bake for about 25 minutes, until golden brown on top.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Based on this recipe: http://www.instructables.com/id/How-To-Make-Bread-without-a-bread-machine/ 
    \begin{itemize}
        \item Main difference is olive oil instead of vegetable oil and honey rather than sugar.
    \end{itemize}
    \item The first time I made this I used cooking spray rather than oil on the pans, it worked fine.
    \item I only have one bread pan, so I put \( \frac{1}{3} \) of the dough into that, and the other \( \frac{2}{3} \) as a larger piece into a shallow pie pan, made for a large roundish loaf.
\end{itemize}
\end{multicols}
\clearpage